### 2007-01-11 Documentation/Manual.tex
*** empty log message ***

\paragraph{Note:} All examples for application software in C do require
a C++ compiler to be properly compiled. For pedagogical reasons, variable
declarations are done at that place where the variable is needed for the
first time, which is at variance with C syntax but not with C++ syntax.
That is the only way in which the examples deviate form ISO C. Moreover
the actual numerical values of the results of the examples may be different
from the ones in this manual.  (IS THAT STILL SO? [WW])

>>>>

% THE FOLLOWING HAS CHANGED: C99, COMPILED WITH GCC; MAYBE ONLY PROBLEMS WITH C89
%
% \paragraph{Note:} All examples for application software in C do require
% a C++ compiler to be properly compiled. For pedagogical reasons, variable
% declarations are done at that place where the variable is needed for the
% first time, which is at variance with C syntax but not with C++ syntax.
% That is the only way in which the examples deviate form ISO C. Moreover
% the actual numerical values of the results of the examples may be different
% from the ones in this manual.
